A Fully Decentralized Infrastructure for Automated and Trusted IoT Data Trading

### 2020-06-04 paper.tex
Cite IPFS in first appearance

In the following researches, IOTA MAM is regarded as a secure data storage which provides access control, tamperproof and authentication functionalities. IOTA is a DAG-based DLT that allows attaching zero value trasactions (i.e., messages) with no transaction fee, and MAM is a protocol that links the messages which forms a channel and endpoint. \cite{luDecentralizedDM} builds the data exchange system with MAM and IPFS, a content-based addressing distributed storage system. Considering the limited transaction processing capability of IOTA, the authors suggest to adopt IPFS to handle the encrypted large data sets, then add the encrypted IPFS link to MAM channel for further exchangement. This research focuses on secure data exchanging architecture design and security analysis, but the trading strategies are not studied yet.

@@

\subsection{Distributed Storage System}
Decentralized storage systems allow users to store files in a distributed network that is maintained by individual nodes around the world instead of a central service provider. Nevertheless, DLTs are often used as the backbone of these systems as data storage and also an incentive layer to encourage people get involved in the network. Filecoin \cite{FileCoin} in Inter-Planetary File system(IPFS)\cite{IPFS} is an incentive layer to incent nodes to provide storage. IPFS is a content-based addressing storage model in a peer-to-peer network, which users can obtain the data with the unique hash value through the network. However, no cryptographic system is applied for user-uploaded files. Sia\cite{Sia} splits the uploaded file into multiple data segments encrypted with the owner's private key, then cipher text is sent to the Sia nodes that rent the storage in Siacoin through smart contracts. Files are duplicated in multiple nodes to prevent data loss.

>>>>

In the following researches, IOTA MAM is regarded as a secure data storage which provides access control, tamperproof and authentication functionalities. IOTA is a DAG-based DLT that allows attaching zero value trasactions (i.e., messages) with no transaction fee, and MAM is a protocol that links the messages which forms a channel and endpoint. \cite{luDecentralizedDM} builds the data exchange system with MAM and IPFS\cite{IPFS}, a content-based addressing distributed storage system. Considering the limited transaction processing capability of IOTA, the authors suggest to adopt IPFS to handle the encrypted large data sets, then add the encrypted IPFS link to MAM channel for further exchangement. This research focuses on secure data exchanging architecture design and security analysis, but the trading strategies are not studied yet.

@@

\subsection{Distributed Storage System}
Decentralized storage systems allow users to store files in a distributed network that is maintained by individual nodes around the world instead of a central service provider. Nevertheless, DLTs are often used as the backbone of these systems as data storage and also an incentive layer to encourage people get involved in the network. Filecoin \cite{FileCoin} in Inter-Planetary File system (IPFS) is an incentive layer to incent nodes to provide storage. IPFS is a content-based addressing storage model in a peer-to-peer network, which users can obtain the data with the unique hash value through the network. However, no cryptographic system is applied for user-uploaded files. Sia\cite{Sia} splits the uploaded file into multiple data segments encrypted with the owner's private key, then cipher text is sent to the Sia nodes that rent the storage in Siacoin through smart contracts. Files are duplicated in multiple nodes to prevent data loss.
